\subsubsection*{Ajax}
Ajax (short for asynchronous JavaScript and XML) is a set of web development techniques using many web technologies on the client side to create asynchronous web applications.

\subsubsection*{AngularJS}
AngularJS is a JavaScript-based open-source front-end web framework mainly maintained by Google and by a community of individuals and corporations to address many of the challenges encountered in developing single-page applications.

\subsubsection*{Application Programming Interface (API)}
In computer programming, an API is a set of subroutine definitions, communication protocols, and tools for building software. In general terms, it is a set of clearly defined methods of communication among various components.

\subsubsection*{Canvas}
Canvas is an HTML element which can be used to draw graphics via scripting (usually JavaScript). This can, for instance, be used to draw graphs, combine photos, or create simple (and not so simple) animations.

\subsubsection*{Endpoints}
Endpoints are important aspects of interacting with server-side web APIs, as they specify where resources lie that can be accessed by third-party software. Usually, the access is via a URI to which HTTP requests are posted, and from which the response is thus expected.

\subsubsection*{Express}
Express is a minimal and flexible Node.js web application framework that provides a robust set of features for web and mobile applications.

\subsubsection*{Functional Requirements}
In software engineering and systems engineering, a functional requirement defines a function of a system or its component, where a function is described as a specification of behavior between outputs and inputs.

\subsubsection*{Graphical User Interface (GUI)}
The GUI is a form of user interface that allows users to interact with electronic devices through graphical icons and visual indicators such as secondary notation, instead of text-based user interfaces, typed command labels or text navigation.

\subsubsection*{MongoDB}
MongoDB is a cross-platform document-oriented database program. Classified as a NoSQL database program, MongoDB uses JSON-like documents with schemata.

\subsubsection*{Node.js}
Node.js is an open-source, cross-platform JavaScript run-time environment that executes JavaScript code outside of a browser.

\subsubsection*{Non-Functional Requirements (NFR)}
In systems engineering and requirements engineering, a non-functional requirement is a requirement that specifies criteria that can be used to judge the operation of a system, rather than specific behaviors.

\subsubsection*{NoSQL}
NoSQL is an approach to database design that can accommodate a wide variety of data models, including key-value, document, columnar and graph formats.

\subsubsection*{Object Related Mapping (ORM)}
Object-relational mapping (ORM, O/RM, and O/R mapping tool) in computer science is a programming technique for converting data between incompatible type systems using object-oriented programming languages.

\subsubsection*{Representational State Transfer (REST)}
REST is a software architectural style that defines a set of constraints to be used for creating Web services.

\subsubsection*{Scalable Vector Graphics (SVG)}
SVG is an XML-based vector image format for two-dimensional graphics with support for interactivity and animation.

\subsubsection*{Single Page Application (SPA)}
A SPA is a web application or web site that interacts with the user by dynamically rewriting the current page rather than loading entire new pages from a server.

\subsubsection*{Software Life Cycle Model (SDLC)}
The SDLC is a term used in systems engineering, information systems, and software engineering to describe a process for planning, creating, testing, and deploying an information system.

\subsubsection*{Stakeholder}
The stakeholder (also project stakeholder) is an individual, group, or organization, who may affect, be affected by, or perceive itself to be affected by a decision, activity, or outcome of a project.

\subsubsection*{Web API}
A Web API is an application programming interface for either a web server or a web browser.
